Using Monte Carlo Algorithms to Achieve Resiliency \& Performance at Scale for Linear and Nonlinear Solver Applications

### 2016-01-26 doc/ecp/pres.tex
Modifying polynomial MCSA slides.

\begin{frame}{Monte Carlo as Approximate Polynomial Preconditioning}
  \begin{itemize}
    \item Using history length cutoff, Monte Carlo process is approximating
      a fixed length Neumann series polynomial
      \[
      x_i = \sum_{k=0}^{\infty}\sum_{i_1}^{N}\sum_{i_2}^{N}\ldots
      \sum_{i_k}^{N}h_{i,i_1}h_{i_1,i_2}\ldots h_{i_{k-1},i_k}b_{i_k}
      \]
    \vfill
    \item As number of histories grows, iteration count becomes identical to
      using ``true'' polynomial
    \vfill
    \item Why limit ourselves to the Neumann series polynomial?
      \begin{itemize}
        \item Chebyshev or GMRES polynomials are viable alternatives
      \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{Neumann Series Polynomial}
  \begin{table}
    \caption{Adjoint MCSA with Neumann Polynomial, $1000 \times 1000$ Shifted Laplacian Matrix.
      Values are MCSA iteration counts (timing in milliseconds)
      \label{tab:lap_adjoint_neumann}}
    \centering
    \begin{tabular}{cccc}
      \toprule
      Histories per & \multicolumn{3}{c}{Polynomial Order} \\
      \cmidrule(lr){2-4}
      Iteration & 2 & 4 & 6 \\
      \midrule
      250 &  775(100) & 651(96) & 664(110) \\
      500 &  725(122) & 502(104) & 394(95) \\
      1000 & 707(174) & 482(179) & 366(144) \\
      2000 & 703(280) & 471(259) & 356(251) \\
      4000 & 698(494) & 467(497) & 350(458) \\
      8000 & 697(923) & 464(905) & 350(873) \\
      16000 & 695(1796) & 462(1768) & 347(1711) \\
      \bottomrule
    \end{tabular}
  \end{table}
\end{frame}

\begin{frame}{Chebyshev Polynomial}
  \begin{table}
    \caption{Adjoint MCSA with Chebyshev Polynomial, $1000 \times 1000$ Shifted Laplacian Matrix.
      Values are MCSA iteration counts (timing in milliseconds)
      \label{tab:lap_adjoint_cheby}}
    \centering
    \begin{tabular}{cccc}
      \toprule
      Histories per & \multicolumn{3}{c}{Polynomial Order} \\
      \cmidrule(lr){2-4}
      Iteration & 1 & 2 & 3 \\
      \midrule
      250 & - & - & - \\
      500 & - & - & - \\
      1000 & - & - & - \\
      2000 & - & 328(134) & - \\
      4000 & - & 296(210) & - \\
      8000 & - & 288(380) & 262(423) \\
      16000 & 1132(1866) & 283(721) & 175(550) \\
      \bottomrule
    \end{tabular}
  \end{table}
\end{frame}

>>>>

\begin{frame}{Monte Carlo as Approximate Polynomial Preconditioning}
  \begin{itemize}
    \item Using history length cutoff, Monte Carlo process is approximating
      a fixed length Neumann series polynomial
    \vfill
    \item Why limit ourselves to the Neumann series polynomial?
      \begin{itemize}
        \item Chebyshev or GMRES polynomials are viable alternatives
      \end{itemize}
  \end{itemize}

  \begin{table}
    \caption{Polynomial MCSA - Shifted Laplacian}
    \centering
    \begin{tabular}{cccc}
      \toprule
      Polynomial & Polynomial & MCSA & Histories per \\
      Type & Order & Iterations & Iteration \\
      \midrule
      Neumann & 4 & 502 & 500 \\
      Chebyshev & 4 & 246 & 16000 \\
      GMRES & 4 & 260 & 2000 \\
      \bottomrule
    \end{tabular}
  \end{table}
\end{frame}
